target_offtarget

### 2025-04-14 manuscript_figures.Rmd
changed lines to lm

background_counts_reads <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(matched),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid(Background ~ type, labeller = as_labeller(facet_names_bg)) +
  theme_few() +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels =
      c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
      )
  ) +
  scale_x_log10(labels = scales::label_log10()) +
  ylab("Log (Viral Reads)")

backgrounds_counts_reads_norm <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(norm_counts1),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid(Background ~ type, labeller = as_labeller(facet_names_bg)) +
  theme_bw() +
  theme_few() +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_x_log10(label = scales::label_log10()) +
  ylab("Log (viral reads/cleaned reads)")

backgrounds_counts_reads_norm2 <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(norm_counts2),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid(Background ~ type, labeller = as_labeller(facet_names_bg)) +
  theme_few() +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_x_log10(labels = scales::label_log10()) +
  ylab("Log (viral reads/cleaned reads/genome length)")

background_read_depths <- 
  depths_reads |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(mean_depth),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid(Background ~ type, labeller = as_labeller(facet_names_bg)) +
  theme_few() +
  theme(
    axis.title.x = element_blank(),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray"),
    axis.title.y = element_text(size = 10),
    legend.title = element_blank()
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_x_log10(label = scales::label_log10()) +
  ylab("Log (mean read depth)")

@@

dedup_reads <- 
  dedup_viral_reads |>
  filter(Background.sample != "Neg_control") |>
  filter(Background.sample != "Msp_p6") |>
  ggplot(aes(
    x = Viral.load,
    y = (count),
    colour = genus
  )) +
  geom_point() +
  geom_smooth(aes(group = genus, linetype = genome_structure), se = FALSE) +
  facet_grid(target ~ Background.sample, labeller = as_labeller(facet_names)) +
  theme_few() + 
  scale_x_log10() +
  scale_y_log10() +
  ylab("Viral Reads") + 
  xlab("Genome copies") + 
  scale_color_manual(values = cols) +
  scale_linetype_manual(values=c("dotted", "solid")) + 
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + 
    scale_y_log10(labels = scales::trans_format("log10", scales::label_math())) +
  theme(
    axis.title.x = element_text(size = 12),
    # axis.text.x = element_text(hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  )

dedup_prop_viral <-
  dedup_viral_reads |>
  filter(Background.sample != "Neg_control") |>
  filter(Background.sample != "Msp_p6") |>
  ggplot(aes(x = Viral.load, y = prop_viral, colour = genus)) +
  geom_point() +
  geom_smooth(aes(group = genus, linetype = genome_structure), se = FALSE) +
  facet_grid(target ~ Background.sample, labeller = as_labeller(facet_names)) +
  theme_few() + 
  scale_x_log10() +
  scale_y_log10() +
  scale_x_log10(labels = scales::trans_format("log10",
                                              scales::label_math())) + 
  scale_y_log10(labels = scales::trans_format("log10",
                                              scales::label_math())) +
  scale_linetype_manual(values=c("dotted", "solid")) + 
  ylab("Proportion of viral reads") +
  xlab("Genome copies") + 
  scale_color_manual(values = cols) +
    theme(
    axis.title.x = element_text(size = 12),
    # axis.text.x = element_text(angle = 30, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  )

dedup_prop_all <-
  dedup_viral_reads |>
  filter(Background.sample != "Neg_control") |>
  filter(Background.sample != "Msp_p6") |>
  ggplot(aes(x = Viral.load, y = prop_total, colour = genus)) +
  geom_point() +
  geom_smooth(aes(group = genus, linetype = genome_structure), se = FALSE) +
  facet_grid(target ~ Background.sample, labeller = as_labeller(facet_names)) +
  theme_few() + 
  scale_x_log10(labels = scales::trans_format("log10",
                                              scales::label_math())) + 
  scale_y_log10(limits = c(5e-8, 1), breaks = 10**(seq(-6,0,2)),labels = scales::trans_format("log10",
                                              scales::label_math())) +
  scale_linetype_manual(values=c("dotted", "solid")) + 
  ylab("Proportion of total reads") +
  xlab("Genome copies") + 
  scale_color_manual(values = cols) +
    theme(
    axis.title.x = element_text(size = 12),
    # axis.text.x = element_text(angle = 30, hjust = 1),
    axis.title.y = element_text(size = 12),
    axis.text.y = element_text(hjust = 1),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  )

>>>>

background_counts_reads <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(matched),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid(Background ~ type, labeller = as_labeller(facet_names_bg)) +
  theme_few() +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels =
      c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
      )
  ) +
 scale_x_log10(labels = label_log()) +  # scales::label_log10()
  ylab("Log (Viral Reads)")

backgrounds_counts_reads_norm <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(norm_counts1),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid(Background ~ type, labeller = as_labeller(facet_names_bg)) +
  theme_bw() +
  theme_few() +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_x_log10(label = label_log()) + # scales::label_log10()
  ylab("Log (viral reads/cleaned reads)")

backgrounds_counts_reads_norm2 <- 
  counts_reads_norm |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(norm_counts2),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid(Background ~ type, labeller = as_labeller(facet_names_bg)) +
  theme_few() +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = 10),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_x_log10(labels = label_log()) +# scales::label_log10()
  ylab("Log (viral reads/cleaned reads/genome length)")

background_read_depths <- 
  depths_reads |>
  filter(Background != "p6") |>
  filter(Background != "control") |>
  ggplot(aes(
    x = Viral.load,
    y = log10(mean_depth),
    colour = virus
  )) +
  geom_point() +
  geom_smooth(aes(group = virus, linetype = genome_structure), se = FALSE) +
  facet_grid(Background ~ type, labeller = as_labeller(facet_names_bg)) +
  theme_few() +
  theme(
    axis.title.x = element_blank(),
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray"),
    axis.title.y = element_text(size = 10),
    legend.title = element_blank()
  ) +
  scale_color_manual(
    values = cols,
    labels = c(
      "Human adenovirus 40",
      "Human betaherpesvirus",
      "Human respiratory syncytial virus",
      "Influenza B virus",
      "Mammalian orthoreovirus 3",
      "Zika virus"
    )
  ) +
  scale_x_log10(label = label_log()) + # scales::label_log10()
  ylab("Log (mean read depth)")

@@

dedup_reads <- 
  dedup_viral_reads |>
  filter(Background.sample != "Neg_control") |>
  filter(Background.sample != "Msp_p6") |>
  ggplot(aes(
    x = Viral.load,
    y = (count),
    colour = genus
  )) +
  geom_point() +
  geom_smooth(aes(group = genus, linetype = genome_structure), method = lm, se = FALSE) +
  facet_grid(target ~ Background.sample, labeller = as_labeller(facet_names)) +
  theme_few() + 
  scale_x_log10() +
  scale_y_log10() +
  ylab("Viral Reads") + 
  xlab("Genome copies") + 
  scale_color_manual(values = cols) +
  scale_linetype_manual(values=c("dotted", "solid")) + 
  scale_x_log10(labels = scales::trans_format("log10", scales::label_math())) + 
    scale_y_log10(labels = scales::trans_format("log10", scales::label_math())) +
  theme(
    axis.title.x = element_text(size = 12),
    # axis.text.x = element_text(hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  )

dedup_prop_viral <-
  dedup_viral_reads |>
  filter(Background.sample != "Neg_control") |>
  filter(Background.sample != "Msp_p6") |>
  ggplot(aes(x = Viral.load, y = prop_viral, colour = genus)) +
  geom_point() +
  geom_smooth(aes(group = genus, linetype = genome_structure), method = lm, se = FALSE) +
  facet_grid(target ~ Background.sample, labeller = as_labeller(facet_names)) +
  theme_few() + 
  scale_x_log10() +
  scale_y_log10() +
  scale_x_log10(labels = scales::trans_format("log10",
                                              scales::label_math())) + 
  scale_y_log10(labels = scales::trans_format("log10",
                                              scales::label_math())) +
  scale_linetype_manual(values=c("dotted", "solid")) + 
  ylab("Proportion of viral reads") +
  xlab("Genome copies") + 
  scale_color_manual(values = cols) +
    theme(
    axis.title.x = element_text(size = 12),
    # axis.text.x = element_text(angle = 30, hjust = 1),
    axis.title.y = element_text(size = 12),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  )

dedup_prop_all <-
  dedup_viral_reads |>
  filter(Background.sample != "Neg_control") |>
  filter(Background.sample != "Msp_p6") |>
  ggplot(aes(x = Viral.load, y = prop_total, colour = genus)) +
  geom_point() +
  geom_smooth(aes(group = genus, linetype = genome_structure), method = lm, se = FALSE) +
  facet_grid(target ~ Background.sample, labeller = as_labeller(facet_names)) +
  theme_few() + 
  scale_x_log10(labels = scales::trans_format("log10",
                                              scales::label_math())) + 
  scale_y_log10(limits = c(5e-8, 1), breaks = 10**(seq(-6,0,2)),labels = scales::trans_format("log10",
                                              scales::label_math())) +
  scale_linetype_manual(values=c("dotted", "solid")) + 
  ylab("Proportion of total reads") +
  xlab("Genome copies") + 
  scale_color_manual(values = cols) +
    theme(
    axis.title.x = element_text(size = 12),
    # axis.text.x = element_text(angle = 30, hjust = 1),
    axis.title.y = element_text(size = 12),
    axis.text.y = element_text(hjust = 1),
    legend.title = element_blank(),
    legend.position = "top", 
    panel.grid.major = element_line(linewidth=0.1, color = "gray60"),
    panel.grid.minor = element_line(linewidth=0.1, color = "lightgray")
  )
